Bird beak's elaboration and innovation

### 2022-07-22 Analysis/03.1-Elaboration_innovation_analysis[statistics].Rmd
Update 03.1-Elaboration_innovation_analysis[statistics].Rmd

```{r, eval = TRUE, echo = FALSE}
load("../Data/Processed/ellipses_stats.rda")

@@

```{r, eval = TRUE, echo = FALSE, fig.height = 20, fig.width = 8}
# pdf("../Manuscript/Figures/orthogonality.results.pdf", width = 6, height = 15)
source("../Functions/ploting.utilities.R")
## Plot the orthogonality into context
orthogonality <- all_results[, c(1:2, 9:14)]

@@

## Plot frame
par(mar = c(5, 9, 4, 2))
plot(NULL, yaxt = "n", xaxt = "n", ylab = "", xlab = "orthogonality", ylim = c(1,nrow(plot_table)), xlim = c(0,1))
abline(v = 0.5, lwd = 0.5, col = "grey")
abline(v = 0.75, lty = 2, col = "grey", lwd = 0.5)
axis(2, at = nrow(plot_table):1, labels = plot_table$Group, las = 2)
axis(1, at = c(0, 0.5, 1), labels = c(0, 0.5, 1))
## Adding the results

for(i in 1:nrow(plot_table)) {
    add.line(plot_table[i, ], counter = i, col = colours[i], total = nrow(plot_table))
    add.stars(plot_table[i, ], counter = i, col = colours[i], total = nrow(plot_table))
}

@@

legend("topleft", legend = c("Super orders (vs. phylogeny)", "Orders (vs. super orders)", "Orders (vs. phylogeny)", "Suborders (vs. passeriformes)", "Families (vs. suborders)", "Families (vs. passeriformes)"), col = c(gg.color.hue(4)[1], gg.color.hue(4)[2], adjustcolor(gg.color.hue(4)[2], alpha.f = 1/3), gg.color.hue(4)[3], gg.color.hue(4)[4], adjustcolor(gg.color.hue(4)[4], alpha.f = 1/3)), pch = 19, lty = 1, cex = 0.8)
# dev.off()
```

>>>>

```{r, eval = TRUE, echo = FALSE}
load("../Data/Processed/ellipses_stats.rda")
source("../Functions/stats.utilities.R")

@@

```{r, eval = TRUE, echo = FALSE, fig.height = 20, fig.width = 8}
#TODO: make the groups nested in the fable

pdf("../Manuscript/Figures/orthogonality.results.pdf", width = 6, height = 15)
source("../Functions/ploting.utilities.R")
## Plot the orthogonality into context
orthogonality <- all_results[, c(1:2, 9:14, 3, 5)]

@@

## Add the number of species and sd to the group names
convert.spaces <- function(x, max) {
    shifts <- max-nchar(as.character(x))
    if(shifts > 0) {
        return(paste(c(x, rep(" ", shifts)), collapse = ""))
    } else {
        return(x)
    }
}
group_names <- paste0(plot_table$Group, "(n = ", sapply(plot_table$n, convert.spaces, max = 4), " ; sd = ", sapply(round(plot_table$`ellipse sd`, 2), convert.spaces, max = 5), ")")

plot_order <- 1:60
## Nestedness bit (not finished)
# plot_order <- integer()
# ## Super-orders
# for(i in 1:6) {
#     plot_order <- c(plot_order, i) 
#     sub_groups <- which(plot_table$Comparison == plot_table$Group[plot_order[length(plot_order)]])
#     if(length(sub_groups)) {
#         plot_order <- c(plot_order, sub_groups)
#     }
# }
# ## Sub-orders
# for(i in 34:39) {
#     plot_order <- c(plot_order, i) 
#     sub_groups <- which(plot_table$Comparison == plot_table$Group[plot_order[length(plot_order)]])
#     if(length(sub_groups)) {
#         plot_order <- c(plot_order, sub_groups)
#     }
# }

## Plot frame
par(mar = c(5, 17, 4, 2))
plot(NULL, yaxt = "n", xaxt = "n", ylab = "", xlab = "orthogonality", ylim = c(1,nrow(plot_table)), xlim = c(0,1))
abline(v = 0.5, lwd = 0.5, col = "grey")
abline(v = 0.75, lty = 2, col = "grey", lwd = 0.5)
axis(2, at = nrow(plot_table):1, labels = group_names[plot_order], las = 2)
axis(1, at = c(0, 0.5, 1), labels = c(0, 0.5, 1))
## Adding the results
for(i in 1:nrow(plot_table)) {
    add.line (plot_table[plot_order[i], ], counter = i, col = colours[plot_order[i]], total = nrow(plot_table))
    add.stars(plot_table[plot_order[i], ], counter = i, col = colours[plot_order[i]], total = nrow(plot_table))
}

@@

legend("topleft", legend = c("Super orders (vs. phylogeny)", "Orders (vs. super orders)", "Orders (vs. phylogeny)", "Suborders (vs. passeriformes)", "Families (vs. suborders)", "Families (vs. passeriformes)"), col = c(gg.color.hue(4)[1], gg.color.hue(4)[2], adjustcolor(gg.color.hue(4)[2], alpha.f = 1/3), gg.color.hue(4)[3], gg.color.hue(4)[4], adjustcolor(gg.color.hue(4)[4], alpha.f = 1/3)), pch = 19, lty = 1, cex = 0.8)
dev.off()
```
